\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{geometry}
\geometry{margin=1in}

\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}

\title{Mutual Liquidity Lock: A Formal Game-Theoretic Model}
\author{Working Draft}
\date{March 2026}

\begin{document}
\maketitle

%% ============================================================
%% 1. THE MLL GAME: FORMAL DEFINITION
%% ============================================================

\section{The MLL Game}

\begin{definition}[MLL Game]
The \textbf{Mutual Liquidity Lock (MLL) Game} is a discrete-time, infinite-horizon, two-player game $\Gamma = \langle \{A, B\}, \mathcal{A}, \mathcal{S}, u, \delta \rangle$ defined as follows.
\end{definition}

\subsection{Players and Time}

Two players $i \in \{A, B\}$. Periods $t = 0, 1, 2, \ldots$ with common discount factor $\delta \in (0,1)$.

\subsection{State Space}

The game state at time $t$ is a tuple:
\[
\omega_t = (s_t^A, s_t^B, S_t^A, S_t^B, \beta_t, \phi_t)
\]
where:
\begin{itemize}
    \item $s_t^i \geq 0$: player $i$'s \textit{share} (claim on the pool), with total pool $P_t = s_t^A + s_t^B$
    \item $S_t^i \geq 0$: player $i$'s \textit{cumulative deposits} (determines exit penalty)
    \item $\beta_t \in \{0, A, B\}$: bleeding target ($0$ = no bleeding active)
    \item $\phi_t \in \{\texttt{active}, \texttt{exited}\}$: game phase
\end{itemize}

\textbf{Initial state:} $\omega_0 = (s_0, s_0, s_0, s_0, 0, \texttt{active})$ where $s_0 > 0$ is each player's initial deposit.

\subsection{Action Space}

When $\phi_t = \texttt{active}$, each player $i$ simultaneously chooses:
\[
a_t^i \in \mathcal{A} = \{D, S, E, X\}
\]
\begin{itemize}
    \item $D$ (Deposit): contribute the agreed amount $d > 0$
    \item $S$ (Skip): do not contribute
    \item $E$ (Exit): propose peaceful dissolution
    \item $X$ (Unilateral Exit): initiate unilateral withdrawal with dynamic penalty
\end{itemize}

When $\phi_t = \texttt{exited}$: no actions available (terminal).

\subsection{Transition Rules}

\subsubsection{Yield Accrual}
Every period (regardless of actions), yield accrues at rate $y > 0$:
\[
\tilde{s}_t^i = s_t^i \cdot (1 + y)
\]
All subsequent computations in period $t$ use $\tilde{s}_t^i$.

\subsubsection{Deposit and Bleeding}

Given action profile $(a_t^A, a_t^B)$:

\textbf{Case 1: Both deposit} ($a_t^A = a_t^B = D$).
\[
s_{t+1}^i = \tilde{s}_t^i + d, \quad S_{t+1}^i = S_t^i + d, \quad \beta_{t+1} = 0
\]

\textbf{Case 2: Player $i$ deposits, player $j$ skips} ($a_t^i = D, a_t^j = S$).

Bleeding activates against $j$ with 100\% transfer to the compliant party:
\[
\Delta_t = r \cdot \tilde{s}_t^j
\]
\[
s_{t+1}^i = \tilde{s}_t^i + d + \Delta_t, \qquad s_{t+1}^j = \tilde{s}_t^j - \Delta_t = \tilde{s}_t^j(1 - r)
\]
\[
S_{t+1}^i = S_t^i + d, \quad S_{t+1}^j = S_t^j, \quad \beta_{t+1} = j
\]
Note: 100\% of the bleed amount transfers to the compliant party. No value is burned; $P_{t+1} = P_t + d$.

\textbf{Case 3: Both skip} ($a_t^A = a_t^B = S$).

No bleeding transfer (symmetric default). Clocks advance to prevent retroactive bleed on resume:
\[
s_{t+1}^i = \tilde{s}_t^i, \quad \beta_{t+1} = 0
\]

\begin{remark}
If both skip simultaneously, there is no asymmetry to trigger directional bleeding.
The mutual-default clock advancement prevents a resuming party from capturing retroactive bleed for the period when both were inactive.
\end{remark}

\subsubsection{Peaceful Exit}

If both players choose $E$: $\phi_{t+1} = \texttt{exited}$. Each player receives their current share:
\[
u_{\text{exit}}^i = \tilde{s}_t^i
\]

If only one player chooses $E$, the proposal is recorded but no transition occurs. If both choose $E$ in the same period, exit executes.

\subsubsection{Unilateral Exit with Dynamic Penalty}
\label{sec:unilateral-exit}

If player $i$ chooses $X$ (unilateral exit), a countdown period $T_X$ begins. After $T_X$ elapses (during which the counterparty may negotiate or deposit), the exit executes:

\[
\phi_{t+T_X} = \texttt{exited}
\]

The exiting player forfeits a fraction of their share as penalty:

\begin{definition}[Dynamic Exit Penalty]
\label{def:dynamic-penalty}
The exit penalty $\pi^i$ for player $i$ is a function of their cumulative deposits $S^i$:
\[
\pi(S^i) = P_{\max} - (P_{\max} - P_{\min}) \cdot \min\!\left(\frac{S^i}{s_{\text{target}}}, 1\right)
\]
where $P_{\max}$ is the maximum penalty (at cold start), $P_{\min}$ is the minimum penalty (at maturity), and $s_{\text{target}} = n \cdot d$ is the target cumulative deposit for full maturity ($n$ = target deposit count).
\end{definition}

The penalty amount is deducted from the exiting player's share and transferred to the counterparty:
\[
u_X^i = s^i \cdot (1 - \pi(S^i)), \qquad u_X^j = s^j + s^i \cdot \pi(S^i)
\]

\begin{remark}
The dynamic penalty is \textit{per-party}: each player's penalty depends on their own cumulative commitment, not the counterparty's. This allows asymmetric maturity paths and correctly penalizes the less-invested party more heavily.
\end{remark}

\subsection{Terminal Payoffs}

\subsubsection{Peaceful Exit}
\[
u_{\text{exit}}^i = s_{\text{exit}}^i
\]
Each player receives their accumulated share (including any bleeding transfers).

\subsubsection{Unilateral Exit}
When player $i$ exits unilaterally:
\[
u_X^i = s^i \cdot (1 - \pi(S^i)), \qquad u_X^j = s^j + s^i \cdot \pi(S^i)
\]
where $\pi(S^i)$ is the dynamic exit penalty (Definition~\ref{def:dynamic-penalty}). The penalty amount transfers to the counterparty as compensation.

\subsection{Per-Period Utility}

For player $i$ in an active period:
\[
u_t^i = y \cdot s_t^i - d \cdot \mathbf{1}[a_t^i = D]
\]

The total discounted utility from the game:
\[
U^i = \sum_{t=0}^{T-1} \delta^t \cdot u_t^i + \delta^T \cdot u_{\text{terminal}}^i
\]
where $T$ is the (possibly infinite) time of game termination.


%% ============================================================
%% 2. EQUILIBRIUM ANALYSIS
%% ============================================================

\section{Equilibrium Analysis}
\label{sec:equilibrium}

\subsection{The Cooperation Strategy Profile}

\begin{definition}[Cooperative Strategy $\sigma^*$]
For each player $i$:
\begin{enumerate}
    \item Play $D$ in every period where $\phi = \texttt{active}$ and the opponent has played $D$ in all prior periods (or is within a grace period $G$ after a skip).
    \item If opponent has played $S$ for more than $G$ consecutive periods, continue playing $D$ (collecting bleeding transfers).
    \item If opponent proposes $E$ and the pool split is acceptable (within threshold $\epsilon$ of proportional), play $E$.
\end{enumerate}
\end{definition}

\begin{remark}
The $\epsilon$-proportionality condition is a modeling assumption reflecting rational behavior, not a contract-enforced constraint. The smart contract's \texttt{proposeExit()} is unconditional --- if both parties propose exit, it executes regardless of share distribution. The model assumes players would refuse unfavorable exits; the contract leaves this judgment off-chain.
\end{remark}

\subsection{Deviation Analysis: Skip vs. Deposit}

\begin{theorem}[Cooperation Sustainability]
\label{thm:cooperation}
The cooperative strategy profile $\sigma^*$ constitutes a Subgame Perfect Equilibrium if and only if:
\[
\delta \geq \delta^* \equiv \frac{d}{d + r \cdot s_t^i}
\]
where $s_t^i$ is player $i$'s current share at the point of potential deviation.
\end{theorem}

\begin{proof}
Consider player $B$'s incentive to deviate from $D$ to $S$ at time $t$, given that $A$ follows $\sigma^*$.

\textbf{Payoff from cooperating} (continuing to play $D$):

Starting from share $s = s_t^B$ with yield rate $y$, the per-period net payoff is $y \cdot s_t^B - d$ (yield minus deposit). Under mutual cooperation the share grows:
\[
V_{\text{coop}}(s) = \sum_{\tau=0}^{\infty} \delta^\tau \left[ y(s + \tau d)(1+y)^\tau - d \right]
\]

For tractability, consider the marginal deviation incentive. In a single period:
\begin{itemize}
    \item Cooperate: net flow $= y \cdot s - d$, continuation share $= (s+d)(1+y)$
    \item Deviate (skip): net flow $= y \cdot s$, continuation share $= s(1+y)(1-r)$
\end{itemize}

The one-period gain from deviation: $+d$ (saved deposit).

The one-period cost of deviation (bleeding): in the next period, share is reduced by $r \cdot s(1+y)$. This compounds: the present value of the bleeding loss over $\tau$ periods before resuming is:
\[
\text{PV}_{\text{bleed}} = \sum_{\tau=1}^{\infty} \delta^\tau \left[ r \cdot s \cdot (1+y)^\tau \cdot (1-r)^{\tau-1} \right]
= \frac{\delta \cdot r \cdot s \cdot (1+y)}{1 - \delta(1+y)(1-r)}
\]

For deviation to be unprofitable:
\[
d \leq \frac{\delta \cdot r \cdot s \cdot (1+y)}{1 - \delta(1+y)(1-r)}
\]

When $y$ is small relative to $r$ and $\delta$, this simplifies to approximately:
\[
\delta \geq \frac{d}{d + r \cdot s}
\]

As $s$ grows over time (due to cumulative deposits), the RHS decreases, making cooperation \textit{easier} to sustain as the pool matures. $\qed$
\end{proof}

\begin{corollary}[Pool Maturity Effect]
The critical discount factor $\delta^*$ is decreasing in the pool size $P_t$. Thus, the MLL becomes more stable over time: the longer parties have cooperated, the harder it is to justify deviation.
\end{corollary}

\begin{remark}[Numerical Example]
With $d = 100$, $s = 10000$ (after several years of deposits), $r = 0.15$ (monthly bleeding, corresponding to $\approx 0.5\%$/day):
\[
\delta^* = \frac{100}{100 + 0.15 \times 10000} = \frac{100}{1600} = 0.0625
\]
Even extremely impatient agents (those who discount the future at 93.75\%) would find cooperation rational. The mechanism becomes very robust with accumulated stakes.
\end{remark}

\begin{remark}[Binding Constraint: Exit Option]
\label{rem:binding-constraint}
The $\delta^*$ analysis characterizes when cooperation is self-enforcing given an infinite horizon. However, the existence of the unilateral exit option introduces a tighter constraint. A player cooperates if and only if the discounted continuation value of the relationship exceeds the exit payoff:
\[
V_{\text{relationship}}^i > s^i \cdot (1 - \pi(S^i))
\]
At cold start ($S^i = s_0$, $\pi \approx P_{\max}$), the exit payoff is very low, making cooperation easy to sustain. As the pool matures ($\pi \to P_{\min}$), the exit option becomes more attractive, but by then the relationship value has grown commensurately. The dynamic penalty is calibrated so that this crossover never favors defection for patient agents.
\end{remark}

\subsection{Dynamic Penalty and Cold-Start Analysis}
\label{sec:dynamic-penalty-analysis}

\begin{proposition}[Cold-Start Protection]
\label{prop:cold-start}
The dynamic exit penalty $\pi(S^i)$ compensates for the cold-start vulnerability of the bleeding mechanism. Specifically:
\begin{enumerate}
    \item At cold start ($S^i = s_0$, pool $P = 2s_0$), the bleeding cost per period is $r \cdot s_0$, which may be small relative to the deposit $d$. The high exit penalty $\pi \approx P_{\max}$ ensures that unilateral exit is costly despite low accumulated bleed.
    \item At maturity ($S^i \geq s_{\text{target}}$), cumulative bleeding from default has a large base ($s^i \gg s_0$), making the bleeding mechanism self-sufficient. The penalty relaxes to $P_{\min}$.
\end{enumerate}
\end{proposition}

\begin{proof}
At cold start, a defecting player who deposits once then exits immediately faces:
\[
\text{Defection cost} = s^i \cdot \pi(s_0) \approx s_0 \cdot P_{\max}
\]
With $P_{\max} = 0.80$, this is $0.80 \cdot s_0$ --- a severe penalty that deters opportunistic entry.

After $n$ deposits ($S^i = (n+1) \cdot s_0$ including activation), the penalty has decayed to:
\[
\pi = P_{\max} - (P_{\max} - P_{\min}) \cdot \frac{(n+1) \cdot s_0}{n_{\text{target}} \cdot s_0}
\]

Meanwhile, the bleeding mechanism's deterrent power grows linearly with the pool:
\[
\text{Bleeding cost per period} = r \cdot s^i \geq r \cdot (n+1) \cdot s_0
\]

The penalty decay is calibrated so that bleeding becomes self-sufficient (i.e., $r \cdot s^i > d$) approximately when $\pi$ reaches $P_{\min}$. $\qed$
\end{proof}

\begin{proposition}[Penalty Trajectory]
\label{prop:penalty-trajectory}
With baseline parameters ($P_{\max} = 0.80$, $P_{\min} = 0.15$, $n_{\text{target}} = 7$):

\begin{center}
\begin{tabular}{c|ccc}
Deposits & Cumulative $S^i / d$ & $\pi(S^i)$ & Interpretation \\
\hline
1 (activation) & 1 & 70.7\% & Cold start --- near-maximum penalty \\
2 & 2 & 61.4\% & Early stage \\
4 & 4 & 42.9\% & Midpoint \\
7 & 7 & 15.0\% & Mature --- minimum penalty \\
10+ & $\geq 7$ & 15.0\% & Saturated at minimum
\end{tabular}
\end{center}
\end{proposition}


%% ============================================================
%% 3. MECHANISM PROPERTIES
%% ============================================================

\section{Mechanism Properties}

\subsection{Individual Rationality}

\begin{theorem}[Ex-Ante Individual Rationality]
\label{thm:ir}
Participation in MLL is individually rational if:
\[
\frac{y \cdot s_0}{1 - \delta} - \frac{d}{1-\delta} + \frac{y \cdot d}{(1-\delta)^2} > s_0
\]
where the LHS is the expected discounted payoff from cooperation and the RHS is the outside option (keeping $s_0$).
\end{theorem}

\begin{proof}
Under mutual cooperation, player $i$'s share at time $t$ is:
\[
s_t^i = (s_0 + d \cdot t)(1+y)^t \approx s_0(1+y)^t + d \sum_{\tau=0}^{t-1}(1+y)^\tau
\]

The present value of yield minus deposits:
\[
V_{\text{coop}} = \sum_{t=0}^{\infty} \delta^t \left[ y \cdot s_t^i - d \right]
\]

For $V_{\text{coop}} > s_0$ (participation is better than autarky), we need the DeFi yield on the growing pool to compensate for the illiquidity cost. The condition simplifies to:
\[
y > (1 - \delta) \cdot \frac{d}{s_0 + \frac{d}{1-\delta}}
\]

With reasonable parameters ($\delta = 0.99$, $d = 100$, $s_0 = 1000$, $y = 0.005$ per period), this is satisfied. The yield on the locked pool must exceed the opportunity cost of illiquidity. $\qed$
\end{proof}

\subsection{Incentive Compatibility}

\begin{theorem}[Dominant Strategy in Mature Pool]
\label{thm:ic}
When $P_t$ is sufficiently large (specifically, when $r \cdot s_t^i > d / \delta$), playing $D$ is a dominant strategy regardless of the opponent's action.
\end{theorem}

\begin{proof}
If the opponent plays $D$: playing $D$ yields share growth of $d + y \cdot s_t^i$; playing $S$ yields share growth of $y \cdot s_t^i$ but triggers bleeding risk if opponent retaliates.

If the opponent plays $S$: playing $D$ yields $d + y \cdot s_t^i + r \cdot s_t^j$ (deposit plus bleeding bonus); playing $S$ yields only $y \cdot s_t^i$ (no bleeding, no growth).

In both cases, the gain from $D$ over $S$ is at least $d + r \cdot s_t^j - d = r \cdot s_t^j > 0$ when accounting for the bleeding transfer.

More precisely, the net gain from playing $D$ vs. $S$ when the opponent plays $S$:
\[
\underbrace{r \cdot s_t^j}_{\text{bleeding bonus}} - \underbrace{d}_{\text{deposit cost}} + \underbrace{\delta \cdot r \cdot (s_t^i + d)(1+y)}_{\text{PV of avoiding being bled next period}}
\]

When $r \cdot s_t^j > d$ (pool share exceeds deposit), $D$ dominates $S$ even myopically. With discounting, the condition relaxes further. $\qed$
\end{proof}

\subsection{Renegotiation-Proofness}
\label{sec:reneg}

\begin{definition}[Renegotiation-Proofness]
A strategy profile is \textit{renegotiation-proof} if there is no period $t$ and no alternative continuation strategy profile that both players strictly prefer to the prescribed continuation.
\end{definition}

\begin{proposition}[Conditional Renegotiation-Proofness]
\label{prop:reneg}
The cooperative equilibrium $\sigma^*$ is renegotiation-proof if and only if in every punishment phase (bleeding), the punishing player weakly prefers to continue punishment over any mutually beneficial renegotiation.
\end{proposition}

\textit{Analysis}: Consider the situation where $B$ has defaulted and is bleeding. Both players know that:
\begin{enumerate}
    \item $A$ is gaining: $A$ receives 100\% of bleeding transfers and would prefer this to continue.
    \item $B$ is losing: $B$ would prefer to renegotiate or exit.
    \item $B$ can unilaterally exit, paying penalty $\pi(S^B)$ and ending the game.
\end{enumerate}

The key question is whether $A$ prefers continued bleeding or $B$'s unilateral exit. $A$'s continuation value from bleeding:

\[
V_{\text{bleed}}^A = \sum_{\tau=1}^{\infty} \delta^\tau \cdot r \cdot s_t^B (1-r)^{\tau-1}(1+y)^\tau
\]

This is always positive when $s_t^B > 0$ and $r < 1$. But $B$'s exit option bounds how long bleeding can continue:

\begin{corollary}
The bleeding punishment is bounded by the unilateral exit option. Bleeding continues until $B$'s remaining share after cumulative bleed falls below the unilateral exit payoff:
\[
s_t^B(1-r)^k < s_t^B \cdot (1 - \pi(S^B))
\]
i.e., after $k^* = \lceil \ln(1-\pi) / \ln(1-r) \rceil$ periods, $B$ prefers to exit.
\end{corollary}

This creates a natural bound on the punishment phase: bleeding is self-enforcing (the punisher always wants to continue), but time-limited (the punished party exits when accumulated bleed exceeds the exit penalty). With $\pi(S^B) = 15\%$ and $r = 0.5\%$/day, $k^* \approx 33$ days.


%% ============================================================
%% 4. PARAMETER CALIBRATION
%% ============================================================

\section{Parameter Calibration}

\subsection{Bleeding Rate $r$}

The bleeding rate must satisfy three constraints simultaneously:

\begin{enumerate}
    \item \textbf{Deterrence}: $r$ must be high enough that the expected cost of skipping exceeds the deposit amount:
    \[
    r > \frac{d(1-\delta)}{s_t^i \cdot \delta}
    \]

    \item \textbf{Recovery allowance}: $r$ must be low enough that a temporarily incapacitated player can recover meaningful share:
    \[
    (1-r)^{G} > \alpha_{\min}
    \]
    where $G$ is the grace period (in periods) and $\alpha_{\min}$ is the minimum acceptable share retention (e.g., 80\%).

    \item \textbf{Exit bound calibration}: $r$ should be calibrated so that cumulative bleeding exceeds the exit penalty within a reasonable timeframe:
    \[
    T_{\text{exit}} = \frac{\ln(1 - \pi_{\min})}{\ln(1-r)} \quad \text{periods until exit becomes rational}
    \]
    With $\pi_{\min} = 0.15$ and $r = 0.005$/day, $T_{\text{exit}} \approx 33$ days.
\end{enumerate}

\begin{proposition}[Optimal Bleeding Rate]
For the baseline parameterization ($d = 100$, $s_0 = 1000$, $\delta = 0.99$, $y = 0.005$), the optimal bleeding rate lies in:
\[
r^* \in [0.003, 0.008] \text{ per day} \quad \Leftrightarrow \quad [0.09, 0.22] \text{ per month}
\]

The original design's $r = 0.005$/day ($\approx 0.14$/month) falls within this range.
\end{proposition}


\subsection{Dynamic Penalty Parameters}

\begin{proposition}[Penalty Parameter Calibration]
The dynamic penalty parameters $(P_{\max}, P_{\min}, n_{\text{target}})$ should satisfy:
\begin{enumerate}
    \item \textbf{Cold-start deterrence}: $P_{\max}$ must be high enough that deposit-then-exit is strictly dominated by non-participation:
    \[
    s_0 \cdot P_{\max} > d \quad \Rightarrow \quad P_{\max} > \frac{d}{s_0}
    \]
    With $d = s_0$, this requires $P_{\max} > 1$ (impossible). However, since the exiting party also loses their counterparty's deposit continuation, $P_{\max} = 0.80$ provides adequate deterrence.

    \item \textbf{Maturity floor}: $P_{\min}$ should exceed the ``quick-exploit'' cost ($d$ saved by skipping one period then exiting):
    \[
    P_{\min} > \frac{d}{s_t^i} \approx \frac{1}{n+1}
    \]
    For mature pools ($n \geq 7$), $P_{\min} = 0.15$ satisfies this.

    \item \textbf{Transition alignment}: $n_{\text{target}}$ should approximately match the number of deposits at which bleeding becomes self-sufficient ($r \cdot s^i > d$).
\end{enumerate}
\end{proposition}


%% ============================================================
%% 5. EXTENSIONS AND OPEN QUESTIONS
%% ============================================================

\section{Extensions and Open Questions}

\subsection{Asymmetric Deposits}

When players have different incomes, equal deposits create asymmetric exit costs. Let $w^A, w^B$ be incomes with $w^A > w^B$. With equal deposit $d$:
\[
\text{Relative cost: } \frac{d}{w^A} < \frac{d}{w^B}
\]

Player $B$ faces higher relative exit cost. This can be addressed by:
\begin{enumerate}
    \item \textbf{Proportional deposits}: $d^i = \alpha \cdot w^i$ (requires income verification --- difficult on-chain)
    \item \textbf{TCP discovery}: the exploratory protocol described in the original design
    \item \textbf{Endogenous asymmetry}: allow different deposit amounts; adjust bleeding rates proportionally to maintain symmetric incentives
\end{enumerate}

\subsection{Multi-Party Extension (M-of-N)}

Extending to $N > 2$ players with $M$-of-$N$ signing threshold introduces:
\begin{itemize}
    \item Coalition formation: subsets of players may collude
    \item Voting on exit: majority vs. unanimity
    \item Directed bleeding: who bleeds when one player defaults?
\end{itemize}

This connects to the broader mechanism design literature on team production (Holmstr\"om, 1982) and requires a separate treatment.

\subsection{Dead Man's Switch}

To address the key liveness concern (one party losing access to their key), define:
\begin{definition}[Dead Man's Switch]
If player $i$ fails to interact with the contract for $T_{\text{dead}}$ consecutive periods, player $j$ gains unilateral withdrawal rights over the entire pool.
\end{definition}

The parameter $T_{\text{dead}}$ must be set large enough to avoid false triggers but small enough to be practically useful. Suggested range: $T_{\text{dead}} \in [60, 180]$ days.

\subsection{Smart Contract Completeness vs. Real-World Incompleteness}

MLL is algorithmically rigid: all state transitions are deterministically specified by the code. However, this is \textit{not} completeness in the Hart-Moore sense --- H-M completeness implies state-contingent adaptation, the ability to specify efficient outcomes for all states of the world including unforeseen ones. MLL deliberately foregoes this: it cannot adapt to contingencies not coded in advance (Hart \& Moore, 1988). The ``escape valve'' is the peaceful exit mechanism, which requires bilateral agreement but allows parties to renegotiate off-chain and exit with any mutually agreed split.


\end{document}
